---
title: "R Notebook"
output: html_notebook
---
The file project_management.csv contains data sampled from the recent work schedule of a small construction company. Column estimated_length contains the estimated length of a building job in days, while column actual_length contains the actual recorded length of the job in days.

We are interested in determining the accuracy of the job estimations made by the company using simple linear regression, so we will eventually want to run a simple linear regression using actual_length as the dependent variable, and estimated_length as the independent variable.

```{r}
library(tidyverse)
library(janitor)
library(modelr)
library(ggfortify)
library(broom)
```


#    Load the data into a dataframe _project_

```{r}
project <- read.csv("6_homework/data/project_management.csv") %>% 
  clean_names()
```


#    Plot the data, taking estimated_length as the independent variable and actual_length as the dependent variable.

```{r}
project %>% 
  ggplot(aes(x = estimated_length, y = actual_length)) +
  geom_point()
```



#    Calculate the correlation coefficient of estimated_length and actual_length and interpret the value you obtain.

```{r}
project %>% 
  summarise(cor(estimated_length, actual_length))

# With a Pearson Correlation Coefficient of 0.8046597 this implies strong positive correlation between the estimated_length and the actual_length
```



#    Perform a simple linear regression using actual_length as the dependent variable, and estimated_length as the independent variable. Save the model object to a variable.

```{r}
project_model <- lm(formula = actual_length ~ estimated_length, data = project)
```


#    Interpret the regression coefficient of estimated_length (i.e. slope, gradient) you obtain from the model. How do you interpret the r2 value reported by the model?

```{r}
project_model %>% 
  glance()

# With an r2 of 0.647 we can say that 64.7% of the variation in actual_length can be predicted from variation in estimated_length
```


#    Is the relationship statistically significant? Remember, to assess this you need to check the p-value of the regression coefficient (or slope/gradient). But you should first check the regression diagnostic plots to see if the p-value will be reliable (don’t worry about any outlier points you see in the diagnostic plots, we’ll return to them in the extension).

```{r}
project_model %>% 
  autoplot()

project_model %>% 
  tidy()

# With a p-value of <0.001 we can say that the relationship is statistically significant
```


#    Return to your plot from earlier, and now label the data points with their row number in the data frame using geom_text() [Hint - you can pass aes(label=1:nrow(project)) to this layer to generate row index labels]

```{r}
project %>% 
  ggplot(aes(x = estimated_length, y = actual_length)) +
  geom_point() +
  geom_text(aes(label = 1:nrow(project)), colour = "red")
```

##    Identify by eye any points you think might be outliers and note their labels.

_5_ maybe _18_ , 31

##    Further split your outliers into those you think are ‘influential’ or ‘non-influential’ based on a visual assessment of their leverage.

Influential
_5_ 
Non-influential
_18_

#    Use your model object from earlier and confirm your visual assessment of which points are ‘influential’ or ‘non-influential’ outliers based on Cook’s distance. You can get a useful plot of Cook’s distance by passing argument which = 4 to autoplot(). Or try the base R plot() function for comparison [e.g. plot(model); you can also use par(mfrow = c(2,2)) just before the plot() command to get a nice two-by-two display]!

```{r}
project_model %>% 
  autoplot(which = 4)
```


#    Obtain the intercept and regression coefficient of variable estimated_length for a simple linear model fitted to data omitting one of your non-influential outlier points.

```{r}
w_outlier <- project %>% 
  summarise(cor(estimated_length, actual_length))

omit_outlier <- project %>% 
  filter(x != "18") %>% 
  summarise(cor(estimated_length, actual_length))
```


##        How different are the intercept and coefficient from those obtained above by fitting the full data set? Does this support classifying the omitted point as non-influential?

```{r}
omit_outlier - w_outlier
```


##        Plot the data points, this regression line and the regression line for the full data set. How different are the lines?

```{r}
project %>% 
  filter(x != "18") %>% 
  ggplot(aes(x = estimated_length, y = actual_length)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

project %>% 
  ggplot(aes(x = estimated_length, y = actual_length)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

#    Repeat the procedure above, but this time omitting one of your influential outliers.
```{r}
project %>% 
  filter(x != "5") %>% 
  ggplot(aes(x = estimated_length, y = actual_length)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

project %>% 
  ggplot(aes(x = estimated_length, y = actual_length)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

