---
title: "R Notebook"
output: html_notebook
---

```{r, echo=FALSE}

library(tidyverse)
library(rpart)
library(rpart.plot)
library(modelr)
library(caret)
library(yardstick)
library(ranger)
library(janitor)
library(GGally)
library(ggfortify)
library(splitstackshape)
library(cluster)
library(factoextra)
library(dendextend)
library(corrplot)

```

## Session 1 -- Clustering & Segmentation Intro

### Learning Outcomes

- Know what _segmentation_ is
- Know what _clustering_ is
- Know the _differences and similarities_ between segmentation and clustering
- Understand the different _types_ of clustering algorithms and their _use cases_

"Manual" process of separating individuals

1. Connectivity models

2. Centroid models : K-means 

3. Distribution models

4. Density models

```{r}

edu_data <- read_csv("2_hierarchical_clustering/data/school_data.csv") %>% 
  clean_names()

```

```{r}

edu_data <- edu_data %>% 
  column_to_rownames("x1")

edu_data %>% 
  skimr::skim()

```

```{r}

edu_data_scale <- edu_data %>% 
  mutate(across(where(is.numeric), scale))


```

```{r}

edu_data_scale %>%
  pivot_longer(cols = everything(),
               names_to = "type", 
               values_to = "value") %>% 
  group_by(type) %>%
  summarise(mean = round(mean(value)), 
            sd = sd(value))

```

```{r}

corrplot(cor(edu_data_scale), method = "number", type = "lower")

```
```{r}
# dissimilarity matrix

dist_matrix <- edu_data_scale %>% 
  select(home_school) %>% 
  get_dist()

dist_matrix
```

```{r}

fviz_dist(dist_matrix)

```

```{r}

clusters <- dist_matrix %>% 
  hclust(method = "complete")

clusters %>% 
  plot(cex = .5, hang = -5)

clustering_dendogram <- clusters %>% 
  as.dendrogram() %>% 
  set("labels_cex", 0.5)

clustering_dendogram %>% 
  plot()
```

```{r}

alt_clusters <-  dist_matrix %>% 
  hclust(method = "ward.D2")

alt_clustering_dendogram <- alt_clusters %>% 
  as.dendrogram() %>% 
  set("labels_cex", 0.5)

clustering_dendogram %>% 
  plot()

dend_diff(clustering_dendogram, alt_clustering_dendogram)
```

```{r}

plot(clusters, cex = .8, hang = -1)
rect.hclust(clusters, k = 2, border = c(2, 4))
  

```

```{r}

edu_clustered_h2 <- edu_data %>% 
  mutate(school_cluster = cutree(clusters, 2))

edu_clustered_h2 %>% 
  ggplot(aes(home_school, state_school, colour = as.factor(school_cluster))) +
  geom_point()

```

```{r}

dist_matrix_state_private <- edu_data_scale %>% 
  select(private_school, state_school) %>% 
  get_dist()

dist_matrix_state_private


state_priv_clusters <-  dist_matrix_state_private %>% 
  hclust(method = "complete")

state_private_dendo <- state_priv_clusters %>% 
  as.dendrogram() %>% 
  set("labels_cex", 0.5)

state_private_dendo %>% 
  plot()

edu_clustered_priv_pub <- edu_data %>% 
  mutate(school_cluster = cutree(state_priv_clusters, 5))


edu_clustered_priv_pub %>% 
  ggplot(aes(private_school, state_school, colour = as.factor(school_cluster))) +
  geom_point()

```

```{r}

dist_matrix_all <- edu_data_scale %>% 
  get_dist()

dist_matrix_all


all_clusters <-  dist_matrix_all %>% 
  hclust(method = "median")

all_dendo <- all_clusters %>% 
  as.dendrogram() %>% 
  set("labels_cex", 0.5)

all_dendo %>% 
  plot()

edu_clustered_all <- edu_data %>% 
  mutate(school_cluster = cutree(all_clusters, 2))


edu_clustered_all %>% 
  ggplot(aes(private_school, state_school, colour = as.factor(school_cluster))) +
  geom_point()


```

```{r}

edu_data_prop <- edu_data %>% 
  mutate(home_prop = home_school / (home_school + state_school + private_school),
         priv_prop = private_school / (home_school + state_school + private_school),
         state_prop = state_school / (home_school + state_school + private_school)) %>%
  select(-c(home_school, state_school, private_school, urban_pop))




dist_matrix_all_prop <- edu_data_scale_prop %>% 
  get_dist()

dist_matrix_all_prop


all_clusters_prop <-  dist_matrix_all_prop %>% 
  hclust(method = "complete")

all_dendo_prop <- all_clusters_prop %>% 
  as.dendrogram() %>% 
  set("labels_cex", 0.5)

all_dendo_prop %>% 
  plot()

edu_clustered_all_prop <- edu_data_prop %>% 
  mutate(school_cluster = cutree(all_clusters_prop, 3))


edu_clustered_all_prop %>% 
  ggplot(aes(priv_prop, state_prop, colour = as.factor(school_cluster))) +
  geom_point()


priv <- edu_clustered_all_prop %>% 
  ggplot() +
  geom_point(aes(school_cluster, priv_prop, colour = as.factor(school_cluster)))

state <- edu_clustered_all_prop %>% 
  ggplot() +
  geom_point(aes(school_cluster, state_prop, colour = as.factor(school_cluster)))

home <- edu_clustered_all_prop %>% 
  ggplot() +
  geom_point(aes(school_cluster, home_prop, colour = as.factor(school_cluster)))

priv
state
home

```

