---
title: "R Notebook"
output: html_notebook
---

# Question 1.

Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.

```{r}

library(tidyverse)
library(CodeClanData)

backpack <- backpack

head(backpack)
dim(backpack)

```


# Question 2.

What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.

```{r}
backpacks <- tibble::rownames_to_column(backpack, var = "student")

backpacks %>% 
  ggplot(aes(backpack_weight)) +
  geom_histogram(col = "white", bins = 20) +
  labs(x = "Number of Students",
       y = "Backpack Weight") +
  scale_y_continuous(breaks = 1:20)

```


# Question 3.

Are there differences in backpack weight between sex?

```{r}

backpacks %>% 
  group_by(sex) %>% 
  mutate(average_weight = mean(backpack_weight)) %>% 
  ggplot(aes(sex, average_weight)) +
  geom_col(position = "dodge") +
  labs(x = "Sex",
       y = "Average Weight of Backpack")
  

```


# Question 4.

What is the relationship between body weight and backpack weight?

```{r}

backpacks %>% 
  ggplot(aes(
    body_weight,
    backpack_weight
  )) +
  geom_point() +
  geom_smooth() +
  labs(x = "Body Weight",
       y = "Backpack Weight")

```


# Question 5.

Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.

```{r}

backpacks %>% 
  ggplot(aes(
    body_weight,
    backpack_weight
  )) +
  geom_point(alpha = 0.2) +
  geom_smooth() +
  facet_wrap(~ sex) +
  labs(x = "Body Weight",
       y = "Backpack Weight") 

```


# Question 6.

What proportion of students report back pain?

```{r}
backpacks %>% 
ggplot() +
  aes(y = year, fill = as.logical(back_problems)) +
  geom_bar() +
  scale_fill_manual(values = c('red', 'blue'),
                    name = '',
                    labels = c('No Backpain', 'Backpain')) +
  labs(x = "Number of Students",
       y = "Year of School")


```


# Question 7.

Is this proportion different between men and women?

```{r}
backpacks %>% 
ggplot() +
  aes(y = year, fill = as.logical(back_problems)) +
  geom_bar() +
  scale_fill_manual(values = c('red', 'blue'),
                    name = '',
                    labels = c('No Backpain', 'Backpain')) +
  facet_wrap(~ sex) +
  labs(x = "Number of Students",
       y = "Year of School")
```


# Question 8.

Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.

Try both backpack_weight and body_weight as well as the ratio.

Hint: faceting would be useful here.