---
title: "R Notebook"
output: html_notebook
---
```{r, echo=FALSE}
library(tidyverse)
library(janitor)
library(GGally)
library(modelr)
library(broom)
library(ggfortify)
library(fastDummies)
```


#    Load the housing_prices.csv data set and undertake an initial exploration of the data. You will find details on the data set on the relevant Kaggle page

```{r}
housing_prices <- read_csv("4_diamonds_hw/data/housing_prices.csv") %>% 
  clean_names()
```


#    We expect the total_rooms of houses to be strongly correlated with total_bedrooms. Use ggpairs() to investigate correlations between these two variables.

```{r, message=FALSE, warning=FALSE}
housing_prices %>% 
  ggpairs()
```


#    So, we do find significant correlations. Let’s drop total_bedrooms from the dataset, and use only total_rooms going forward.

```{r}
housing_prices_clean <- housing_prices %>% 
  select(-total_bedrooms)
```

#    We are interested in developing a regression model for the median_house_value of a house in terms of the possible predictor variables in the dataset.

##    Use ggpairs() to investigate correlations between median_house_value and the predictors (this may take a while to run, don’t worry, make coffee or something).

```{r,warning=FALSE, message=FALSE}
housing_prices_clean %>% 
  ggpairs()

# median_income has a strong correlation and total_rooms has a small positive correlatin, and latitude has a small negative correlation
```


##    Perform further ggplot visualisations of any significant correlations you find.

```{r}

housing_prices %>% 
  ggplot(aes(median_house_value, median_income)) +
  geom_point() +
  geom_smooth(method = "lm")

housing_prices %>% 
  ggplot(aes(median_house_value, total_rooms)) +
  geom_point() +
  geom_smooth(method = "lm")

housing_prices %>% 
  ggplot(aes(median_house_value, latitude)) +
  geom_point() +
  geom_smooth(method = "lm")

```


#    Shortly we may try a regression model to fit the categorical predictor ocean_proximity. Investigate the level of ocean_proximity predictors. How many dummy variables do you expect to get from it?

```{r, warning=FALSE, message=FALSE}
housing_prices_clean %>% 
  count(ocean_proximity)

housing_prices_dummy %>% 
  count(ocean_proximity)

housing_prices_clean %>% 
  select(ocean_proximity) %>% 
  factor()

housing_prices_dummy <- housing_prices_clean %>%
  mutate(ocean_proximity = recode(ocean_proximity, "ISLAND" = "NEAR OCEAN")) %>% 
  fastDummies::dummy_cols(select_columns = "ocean_proximity", 
                          remove_first_dummy = TRUE, 
                          remove_selected_columns = TRUE) %>% 
  clean_names()


housing_prices_dummy %>% 
  select(median_house_value, starts_with("ocean_")) %>% 
  ggpairs()
# Expect to get 4 dummy variables or 3 after recoding as island had only 5 objects
```



#    Start with simple linear regression. Regress median_house_value on median_income and check the regression diagnostics.

```{r}

lm1 <- lm(median_house_value ~ median_income, housing_prices_clean)

lm1 %>% 
  autoplot()

lm1 %>% 
  summary()


```


#    Add another predictor of your choice. Check your assumptions, diagnostics, and interpret the model.

```{r}
lm2 <- lm(median_house_value ~ median_income + latitude + ocean_proximity_near_bay , housing_prices_dummy)

lm2 %>% 
  autoplot()

lm2 %>% 
  summary()

# With every increase in median income by $10000 we expect to see an increase in median house value of $38646 with all other predictors remaining constant

# With every degree of latitude increase we see a decrease in median house value of $7445 with all other predictors remaining constant

# Being "near the bay" we expect to see a increase in median house value of $58389

# The r2 value tells us that approximately 45% of the variation in median house value can be predicted by the variations in median income, latitude and proximity to ocean  


```

