---
title: "R Notebook"
output: html_notebook
---
```{r, echo=FALSE}

library(tidyverse)
library(rpart)
library(rpart.plot)
library(modelr)
library(caret)
library(yardstick)
library(ranger)
library(janitor)
library(GGally)
library(ggfortify)
library(splitstackshape)
library(cluster)
library(factoextra)
library(dendextend)
library(corrplot)
library(broom)
library(shiny)

```

#    You have been provided some customer data from a shopping centre. Do some exploratory analysis on the data. Comment on findings.

```{r}

customers <- read_csv("data/mall_customers.csv") %>% 
  clean_names()

head(customers)
skimr::skim(customers)

customers %>% 
  ggplot() +
  aes(age) +
  geom_point(aes(y = spending_score_1_100), colour = "blue")

# very clear drop in spending score around 40

customers %>% 
  ggplot() +
  aes(gender) +
  geom_jitter(aes(y = annual_income_k), colour = "dark green")

customers %>% 
  ggplot() +
  aes(gender) +
  geom_jitter(aes(y = spending_score_1_100), colour = "dark green")
# 

scaled_customers <- customers %>% 
  column_to_rownames("customer_id") %>% 
  mutate(across(where(is.numeric), scale)) %>% 
  select(-gender, -age)

```


#    We are interested in creating a marketing campaign to target customers based on their spending score and annual income. Perform a k-means clustering to find if there are meaningful clusters in the data to target the customers.

#    Perform k-means clustering and chose a value of k.

```{r}

fviz_nbclust(scaled_customers, kmeans, method = "silhouette", k.max = 25)

# Silhouette likes 6 clusters, but upon plotting I chose 5 as cluster 6 I felt was not necessary.

max_k <- 10

k_clusters_customers <- tibble(k = 1:max_k) %>%
  mutate(
    kclust = map(k, ~ kmeans(scaled_customers, .x, nstart = 10)), 
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, scaled_customers)
  )

customer_clusterings <- k_clusters_customers %>% 
  unnest(glanced)

```


#    Visualise the clustering for your chosen value of k.

```{r}

customer_clusterings %>% 
  unnest(cols = augmented) %>% 
  filter(k == 5) %>% 
  ggplot() +
  aes(annual_income_k, spending_score_1_100, colour = .cluster) +
  geom_point()

```


#    Do you think the clustering seems a good fit for this data?

I would say the clustering is an excellent fit for this data

#    Comment on the attributes on one or two of the clusters (maybe even give them a label if you like - like in section 4.1 of the ‘Segmentation & clustering intro’ lesson).

```{r}
cluster_lab <- customer_clusterings %>%
  filter(k == 5) %>% 
  unnest(cols = augmented) %>% 
  select(.cluster)

customer_w_clusters <- customers %>% 
  bind_cols(cluster_lab)

customer_w_clusters %>% 
  ggplot() +
  aes(x = annual_income_k, y = spending_score_1_100, colour = .cluster) +
  geom_point() 
```

Cluster 1 could be tight budgeted
Cluster 2 could be average joes
Cluster 3 could be spendthrifts
Cluster 4 could be whales
Cluster 5 could be squanderers

Best option for targetting would be cluster 4, high income and free spending.
Could target cluster 5, but this may be an ethical question, low income, high spending. 

