---
title: "Homework Week5 day 1"
output: html_notebook
---

```{r}
library(CodeClanData)
library(tidyverse)

```

```{r}
qb_revenue_breakdown <- janitor::clean_names(qb_revenue_breakdown)
qb_competitors <- janitor::clean_names(qb_competitors)
qb_device_data <- janitor::clean_names(qb_device_data)
qb_monthly_sales <- janitor::clean_names(qb_monthly_sales)

col_scheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")
```


# Part 1
## Question 1.
Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset.

```{r}
qb_revenue_breakdown %>% 
  ggplot(aes(x = year,
             fill = product)) +
  geom_bar() +
  theme(panel.border = element_rect(colour = "#B6A7B5", 
                                fill = NA, 
                                linetype = 2),
    # color background 2)
    panel.background = element_rect(fill = "white"),
    # modify grid 3)
    panel.grid.major.x = element_line(colour = "#B6A7B5", 
                                      linetype = 3, 
                                      size = 0.5),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y =  element_line(colour = "#B6A7B5", 
                                       linetype = 3, 
                                       size = 0.5),
    panel.grid.minor.y = element_blank()) +
  scale_fill_manual(values = col_scheme)
```

## Question 2.
Make a line chart showing monthly sales of the “flagship product” - the ‘KwikBit Unit 1’ - over the last year. This data is inside qb_monthly_sales, but you will need to use filter() or subset() (base R).

```{r}

qb_monthly_sales %>% 
  filter(cashflow == "Kwikbit Unit 1 Sales") %>% 
  ggplot(aes(x = date,
             y = amount,
             colour = cashflow)) +
  geom_line() +
  theme(panel.border = element_rect(colour = "#B6A7B5", 
                                fill = NA, 
                                linetype = 2),
    # color background 2)
    panel.background = element_rect(fill = "white"),
    # modify grid 3)
    panel.grid.major.x = element_line(colour = "#B6A7B5", 
                                      linetype = 3, 
                                      size = 0.5),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y =  element_line(colour = "#B6A7B5", 
                                       linetype = 3, 
                                       size = 0.5),
    panel.grid.minor.y = element_blank()) +
  scale_colour_manual(values = col_scheme) 
  
```


## Question 3.
Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales.

```{r}
qb_monthly_sales %>% 
  filter(cashflow != "Kwikbit Unit 1 Sales") %>% 
  ggplot(aes(x = date,
             y = amount,
             colour = cashflow)) +
  geom_line(aes(group = cashflow)) +
  labs(x = "\nYear", 
       y = "Sales\n",
       title = "Qikbit revenue vs cost\n",
       fill = " ") +
  theme(panel.border = element_rect(colour = "#B6A7B5", 
                                fill = NA, 
                                linetype = 2),
    # color background 2)
    panel.background = element_rect(fill = "white"),
    # modify grid 3)
    panel.grid.major.x = element_line(colour = "#B6A7B5", 
                                      linetype = 3, 
                                      size = 0.5),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y =  element_line(colour = "#B6A7B5", 
                                       linetype = 3, 
                                       size = 0.5),
    panel.grid.minor.y = element_blank()) +
  scale_colour_manual(values = col_scheme)
```


## Question 4.
Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors.

```{r}

qb_competitors %>% 
  ggplot(aes(x = year,
             fill = company,
             y = revenue)) +
  geom_area() +
  labs(x = "\nYear", 
       y = "Revenue\n",
       title = "Fitness tracker market share\n",
       fill = "Companies") +
  theme(panel.border = element_rect(colour = "#B6A7B5", 
                                fill = NA, 
                                linetype = 2),
    # color background 2)
    panel.background = element_rect(fill = "white"),
    # modify grid 3)
    panel.grid.major.x = element_line(colour = "#B6A7B5", 
                                      linetype = 3, 
                                      size = 0.5),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y =  element_line(colour = "#B6A7B5", 
                                       linetype = 3, 
                                       size = 0.5),
    panel.grid.minor.y = element_blank()) +
  scale_fill_manual(values = col_scheme)

```


## Question 5.
Now show the sales from the four competitors as a line graph. Include an extra layer that shows the data points used to make the lines.

```{r}

qb_competitors %>% 
  ggplot(aes(x = year,
             y = revenue
             )) +
  aes(colour = company)+
  geom_line() +
  geom_point() +
  labs(x = "\nYear", 
       y = "Revenue\n",
       title = "Qikbit revenue vs leading competition\n",
       fill = "Companies") +
  theme(panel.border = element_rect(colour = "#B6A7B5", 
                                fill = NA, 
                                linetype = 2),
    # color background 2)
    panel.background = element_rect(fill = "white"),
    # modify grid 3)
    panel.grid.major.x = element_line(colour = "#B6A7B5", 
                                      linetype = 3, 
                                      size = 0.5),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y =  element_line(colour = "#B6A7B5", 
                                       linetype = 3, 
                                       size = 0.5),
    panel.grid.minor.y = element_blank()) +
  scale_colour_manual(values = col_scheme)
 
```


## Question 6.
Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between companies and people. The data for this is in qb_device_data.

```{r}

cumul_device_data <- qb_device_data %>% 
  group_by(device, id) %>% 
  mutate(time = hours * 60 + mins,
         cumulative_steps = cumsum(counts)) %>% 
  unnest(cols = c())


cumul_device_data %>% 
  ggplot(aes(x = time,
             y = cumulative_steps
             )) +
  aes(colour = device) +
  geom_line(alpha = 0) +
  geom_smooth() +
  facet_grid(device ~ id) +
  scale_colour_manual(values = col_scheme) +
  labs(x = "\nTime", 
       y = "Steps\n",
       title = "Qikbit vs other leading brands",,
       fill = "Companies")

```


# 2.2 Part 2

## Question 1.
Take the plots that you produced in part one and now polish them by:

  Adding appropriate labels
  Changing the scales and coordinates when appropriate.
  Applying a unified theme, which is described below:
  Graphs should have white backgrounds, and use colour sparingly.
  There should be faint grid lines.
  Font sizes should be ~12pt although titles should be slightly larger and axis          labels can be slightly smaller.
  All plots should use colours from the following company colour scheme.

```{r}
qikbit_theme <- function() {
  theme(panel.border = element_rect(colour = "#B6A7B5", 
                                fill = NA, 
                                linetype = 2),
    # color background 2)
    panel.background = element_rect(fill = "white"),
    # modify grid 3)
    panel.grid.major.x = element_line(colour = "#B6A7B5", 
                                      linetype = 3, 
                                      size = 0.5),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y =  element_line(colour = "#B6A7B5", 
                                       linetype = 3, 
                                       size = 0.5),
    panel.grid.minor.y = element_blank()),
    axis.text = element_text(size = 12, 
                             colour = "#50434f", 
                             family = "Times New Roman"),
    axis.title = element_text(size = 12, 
                              colour = "#50434f", 
                              family = "Times New Roman"),
    axis.ticks = element_line(colour = "#50434f"),
    legend.position = "bottom"
  )
}


```

