---
title: "R Notebook"
output: html_notebook
---


```{r, echo=FALSE}

source(file = "c:/Users/anomi/OneDrive/Desktop/Repositories/codeclan_homework_ChrisGlenshaw/week_11/day_5/librarys.R")
```

# Read in and clean names
```{r}
orange_juice <- read_csv(here::here("2_logistic_homework/data/orange_juice.csv")) %>% 
  clean_names()
```

# Exploring data
```{r}

orange_juice %>% 
  head()

orange_juice %>% 
  distinct(store7)

orange_juice %>% 
  distinct(store)

orange_juice %>% 
  distinct(store_id)

orange_juice %>% 
  select(weekof_purchase) %>% 
  mutate(weekof_purchase = weekof_purchase - 226) %>% 
  slice_max(weekof_purchase)

```

# alias investigation
```{r}

orange_juice_clean <- orange_juice %>% 
  mutate(is_mm = as.logical(if_else(purchase == "MM", 1, 0)), .before = weekof_purchase) %>% 
  select(-c(purchase, store, store7, list_price_diff, price_diff, sale_price_mm, sale_price_ch))

alias_model <- glm(is_mm ~ .,
                   family = binomial(link = "logit"),
                   data = orange_juice_clean)

alias_model %>% 
  alias()

# Identified store, list_price_diff, price_diff, sale_price_mm, sale_price_ch through alias as superfluous.  Identified store7 as being derived from store_id.  Added all to be deselected.

```


# Test / Train
```{r}
#for consistency only.
set.seed(73)
# create test / train split
n_data <- nrow(orange_juice)

test_index <- sample(1:n_data, size = n_data * .2)

oj_test <- slice(orange_juice, test_index)
oj_train <- slice(orange_juice, -test_index)

# check split balance
oj_test %>% 
  tabyl(purchase)
oj_train %>% 
  tabyl(purchase)

```


# train final cleaning

```{r}
# Following cleaning methods from alias analysis, and setting factors to categorical fields.
oj_train_clean <- oj_train %>% 
  mutate(is_mm = as.logical(if_else(purchase == "MM", 1, 0)), .before = weekof_purchase,
         store_id = as.factor(store_id),
         weekof_purchase = as.factor(weekof_purchase - 226)
         ) %>% 
  select(-c(purchase, store, store7, list_price_diff, price_diff, sale_price_mm, sale_price_ch))

```

# glmulti model building

```{r}

glmulti_oj_fit <- glmulti(
  is_mm ~ ., 
  data = oj_train_clean,
  level = 1,          # 1 = main effects only 
  method = "h",       # exhaustive search
  crit = bic,         # criteria for model selection is BIC value (lower is better)
  plotty = F,         # plot models as function runs
  report = TRUE,      # do produce reports as function runs
  confsetsize = 10,   # return best 10 solutions
  fitfunction = glm,  # fit using the `glm` function
  chunks = 4,         # use 4 processors
  family = binomial(link = "logit")
  )

glmulti_oj_fit %>% 
  summary()

glmulti_oj_fit_1_pair <- glmulti(
  is_mm ~ price_ch + price_mm + disc_ch + disc_mm + loyal_ch, 
  data = oj_train_clean,
  level = 2,          # 1 = main effects only 
  minsize = 6,        # no min size of model
  maxsize = 10,       # -1 = no max size of model
  method = "h",       # exhaustive search
  marginality = TRUE, # ensure using primary predictors where 
  crit = bic,         # criteria for model selection is BIC value (lower is better)
  plotty = F,         # plot models as function runs
  report = TRUE,      # do produce reports as function runs
  confsetsize = 10,   # return best 10 solutions
  fitfunction = glm,  # fit using the `glm` function
  chunks = 4,         # use 4 processors
  family = binomial(link = "logit")
  )




glmulti_oj_fit %>% 
  summary()

glmulti_oj_fit_1_pair %>% 
  summary()

```

# test data clean and model 2 (with 1 pair)
```{r}
# Clean test set
oj_test_clean <- oj_test %>% 
  mutate(is_mm = as.logical(if_else(purchase == "MM", 1, 0)), .before = weekof_purchase,
         store_id = as.factor(store_id),
         weekof_purchase = as.factor(weekof_purchase - 226)
         ) %>% 
  select(-c(purchase, store, store7, list_price_diff, price_diff, sale_price_mm, sale_price_ch))

# run generated model on test set
oj_test_model_1p <- glm(is_mm ~ price_ch + price_mm + disc_ch + disc_mm + loyal_ch + disc_mm:disc_ch,
                     family = binomial(link = "logit"),
                     data = oj_test_clean)

oj_test_model_1p %>% 
  summary()

# add predictions to test dataset
oj_test_clean_pred_1p <- oj_test_clean %>% 
  add_predictions(oj_test_model_1p, type = "response")

# setting prediction threshold, .5 as it is a binary answer.
prediction_threshold <- 0.5

# applying threshold
oj_test_clean_pred_1p_tf <- oj_test_clean_pred_1p %>% 
  mutate(pred_logical = as.factor(pred > prediction_threshold),
         is_mm = as.factor(is_mm))

# Generating confusion matrix
oj_test_clean_pred_1p_tf %>% 
  conf_mat(trut = is_mm, estimate = pred_logical)

# Creating roc object
oj_test_1p_roc <- oj_test_clean_pred_1p_tf %>% 
  roc(response = is_mm,
      predictor = pred)

# plotting ROC curve
roc_curve_1p <- ggroc(oj_test_1p_roc,
                   legacy.axes = TRUE,
                   )+
  coord_fixed() +
  labs(x = "FPR", y = "TPR")

# Checking AUC
auc(oj_test_1p_roc)
```


# test data clean and model 1 (no 1 pair) 
```{r}
# run generated model on test set
oj_test_model <- glm(is_mm ~ price_ch + price_mm + disc_ch + disc_mm + loyal_ch,
                     family = binomial(link = "logit"),
                     data = oj_test_clean)

oj_test_model %>% 
  summary()

# add predictions to test dataset
oj_test_clean_pred <- oj_test_clean %>% 
  add_predictions(oj_test_model, type = "response")

# applying threshold
oj_test_clean_pred_tf <- oj_test_clean_pred %>% 
  mutate(pred_logical = as.factor(pred > prediction_threshold),
         is_mm = as.factor(is_mm))

# Generating confusion matrix
oj_test_clean_pred_tf %>% 
  conf_mat(trut = is_mm, estimate = pred_logical)

# Creating roc object
oj_test_roc <- oj_test_clean_pred_tf %>% 
  roc(response = is_mm,
      predictor = pred)

# plotting ROC curve
roc_curve <- ggroc(data = list(pred1p = oj_test_1p_roc,
                               pred = oj_test_roc),
                   legacy.axes = TRUE,
                   )+
  coord_fixed() +
  labs(x = "FPR", y = "TPR")

# Checking AUC
auc(oj_test_roc)
```

# kfold validation one pair
```{r}
# Clean full dataset
oj_full_clean <- orange_juice %>% 
  mutate(is_mm = as.factor(if_else(purchase == "MM", 1, 0)), .before = weekof_purchase,
         store_id = as.factor(store_id),
         weekof_purchase = as.factor(weekof_purchase - 226)
         ) %>% 
  select(-c(purchase, store, store7, list_price_diff, price_diff, sale_price_mm, sale_price_ch))

cv_10fold <- trainControl(method = "cv", 
                          number = 10,
                          savePredictions = TRUE)


model_1p_kfold <- train(is_mm ~ price_ch + price_mm + disc_ch + disc_mm + loyal_ch + disc_mm:disc_ch,
               data = oj_full_clean,
               trControl = cv_10fold,
               method = "glm",
               family = binomial(link = "logit"))

model_1p_kfold$resample

```

# kfold validation no pair
```{r}
# Clean full dataset
oj_full_clean <- orange_juice %>% 
  mutate(is_mm = as.factor(if_else(purchase == "MM", 1, 0)), .before = weekof_purchase,
         store_id = as.factor(store_id),
         weekof_purchase = as.factor(weekof_purchase - 226)
         ) %>% 
  select(-c(purchase, store, store7, list_price_diff, price_diff, sale_price_mm, sale_price_ch))

model_0p_kfold <- train(is_mm ~ price_ch + price_mm + disc_ch + disc_mm + loyal_ch,
               data = oj_full_clean,
               trControl = cv_10fold,
               method = "glm",
               family = binomial(link = "logit"))

model_0p_kfold$resample

```
# Kfold comparison
```{r}

mean(model_1p_kfold$resample$Accuracy)
mean(model_0p_kfold$resample$Accuracy)

```


## Conclusion
If we are choosing our model purely on higher AUC then we should go with the model including 1 pair. 



# Creating classifier
```{r}

classifier_data <- tibble(
  threshold = oj_test_1p_roc$thresholds,
  TPR_sensitivity = oj_test_1p_roc$sensitivities,
  TNR_specificity = oj_test_1p_roc$specificities)

```

